data_collation

### 2024-05-17 scripts/data_collation.Rmd
updated UPC data

# remove columns with observer and unneeded data
UPC_data <- UPC_data[ -c(21:24) ]

@@

@@

#UPC data frame does not have month and day so that is why it isn't connecting fully
```

@@

@@

# Remove four columns in a specific order FtWeatherill_swath_2016
FtWeatherill_swath_2016 <- FtWeatherill_swath_2016 %>%
  select(-9:-14)

# make columns lowercase
# Get the current column names
current_names <- colnames(FtWeatherill_swath_2016)

# Assign the new column names to the first six columns of the dataframe
colnames(FtWeatherill_swath_2016)[1:6] <- new_names

@@

# Rename ft. wetherill to fort wetherill
swath_data$SITE[swath_data$SITE == "Ft.Weatherill"] <- "Fort Wetherill"

#still need to edit ft.wetherill dataframe

>>>>

# remove columns with observer and unneeded data
UPC_data <- UPC_data[ -c(20:24) ]

@@

# make columns lowercase
# Get the current column names
current_names <- colnames(UPC_data)

# Convert the column names to lowercase while preserving the first letter
new_names <- sapply(current_names[1:13], function(x) {
  paste0(toupper(substring(x, 1, 1)), tolower(substring(x, 2)))
})

# Assign the new column names to the first six columns of the dataframe
colnames(UPC_data)[1:13] <- new_names

@@

@@

FtWeatherill_swath_2016 <- FtWeatherill_swath_2016 %>%
  rename(
    "0-20 IN" = "X0.20.IN",
    "20-40 IN" = "X20.40.IN",
    "40-20 OFF" = "X40.20.OFF",
    "20-0 OFF" = "X20.0.OFF")

@@

# make columns lowercase
# Get the current column names
#current_names <- colnames(FtWeatherill_swath_2016)

# Convert the column names to lowercase while preserving the first letter
#new_names <- sapply(current_names[1:6], function(x) {
#  paste0(toupper(substring(x, 1, 1)), tolower(substring(x, 2)))
#})

# Assign the new column names to the first six columns of the dataframe
#colnames(FtWeatherill_swath_2016)[1:6] <- new_names

@@

# Rename ft. wetherill to fort wetherill
swath_data$Site[swath_data$Site == "Ft.Weatherill"] <- "Fort Wetherill"
